Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 method.tex
Deleted funky indent
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@927 ccdd05d5-56c1-461a-bf98-85f6876523b4
Fixed an error in section 2.1
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@928 ccdd05d5-56c1-461a-bf98-85f6876523b4

Inspiral signals are continuously parameterized by a set of intrinsic source
parameters $\vec\theta$ that determine the amplitude and phase evolution of the
gravitational wave strain. For systems where the effects of spin can be
ignored, the intrinsic source parameters are the component masses of the
binary, $\vec\theta = (m_1, m_2)$. Searches for inspiral signals typically
employ matched filter banks that discretely sample the possible intrinsic
parameters~\cite{findchirppaper}.  For a given source, the strain observed by
the detector is a linear combination of two waveforms corresponding to the
`$+$' and `$\times$' gravitational wave polarizations, so for any value of
$\vec\theta$ we must implement 2 filters.  The coefficients for the $M$ filters
are known as templates, and are formed by discretizing and time reversing the
waveforms and weighting them by the inverse amplitude spectral density of the
detector's noise. To construct a template bank, templates are chosen with the
$M/2$ discrete signal parameters $\vec\theta_0,\, \vec\theta_1,\, \dots,\,
\vec\theta_{M/2-1}$ to assure a bounded loss of \SNR~\cite{Owen:1998dk}. That
is, any possible signal within a given range of intrinsic
source parameters will have an inner product that is $\geqslant 0.97$ with at
least one template. Such a template bank is said to have a {\em minimum match}
of 0.97. The data from the detector are whitened and convolved with each
template to produce $2M$ \SNR\ time series. Local peak-finding across time and
templates determines detection candidates.

>>>>

Inspiral signals are continuously parameterized by a set of intrinsic source
parameters $\vec\theta$ that determine the amplitude and phase evolution of the
gravitational wave strain. For systems where the effects of spin can be
ignored, the intrinsic source parameters are the component masses of the
binary, $\vec\theta = (m_1, m_2)$. Searches for inspiral signals typically
employ matched filter banks that discretely sample the possible intrinsic
parameters~\cite{findchirppaper}.  For a given source, the strain observed by
the detector is a linear combination of two waveforms corresponding to the
`$+$' and `$\times$' gravitational wave polarizations, so for any value of
$\vec\theta$ we must implement 2 filters.  The coefficients for the $\numtmps$ filters
are known as templates, and are formed by discretizing and time reversing the
waveforms and weighting them by the inverse amplitude spectral density of the
detector's noise. To construct a template bank, templates are chosen with the
$\numtmps/2$ discrete signal parameters $\vec\theta_0,\, \vec\theta_1,\, \dots,\,
\vec\theta_{\numtmps/2-1}$ to assure a bounded loss of \SNR~\cite{Owen:1998dk}. That
is, any possible signal within a given range of intrinsic
source parameters will have an inner product that is $\geqslant 0.97$ with at
least one template. Such a template bank is said to have a {\em minimum match}
of 0.97. The data from the detector are whitened and convolved with each
template to produce $\numtmps$ \SNR\ time series. Local peak-finding across time and
templates determines detection candidates.
